The design and implementation of standards-based Grid single sign-on using federated identity

### 2009-05-01 doc/sec/papers/GRID09/paper.tex
little change again

Figure~\ref{fig:TLS_thread_all} shows performance results when secure
communication is used. For Axis2/C, we configure the http server (that hosts Axis2/C) with the SSL
module enabled. Each experiment is executed for a duration of two minutes.
We see that, similarly to Figure~\ref{fig:TCP_thread_all}, response
time of services both in HED and Axis2/C also starts from a similar value (when the number of
clients is five) and changes linearly with the number of clients, while the service in HED also provides much shorter
response time with the value being sightly more than about one third of the response time of
the service in Axis2/C when  number of clients becomes higher.
In the case of throughput, the throughput of service in HED increases linearly
with the client numbers initially, however, it saturates at around 13000 requests per
minutes when the number  of client number is higher than 30. On the other hand, the throughput of service in
Axis2/C saturates already when the number of clients reaches 10, with
the value being around sightly more than one third of the throughput of service in HED.

We conclude that the HED can provide better performance than Axis2/C, in both
cases of secure communication being enabled and disabled, especially when the number of
simultaneous clients is bigger.

>>>>

Figure~\ref{fig:TLS_thread_all} shows performance results when secure
communication is used. For Axis2/C, we configure the http server (that hosts Axis2/C) with the SSL
module enabled. Each experiment is executed for a duration of two minutes.
We see that, similarly to Figure~\ref{fig:TCP_thread_all}, response
time of services both in HED and Axis2/C also starts from a similar value (when the number of
clients is five) and changes linearly with the number of clients, while the service in HED also provides much shorter
response time with the value being sightly more than about one third of the response time of
the service in Axis2/C when  number of clients becomes higher.
In the case of throughput, the throughput of service in HED increases linearly
with the client numbers initially, however, it saturates at around 13000 requests per
minute when the number  of client number is higher than 30. On the other hand, the throughput of service in
Axis2/C saturates already when the number of clients reaches 10, with
the value being around sightly more than one third of the throughput of service in HED.

We conclude that the HED can provide comparable performance 
as Axis2/C, in both cases of secure communication being enabled and disabled.
